Predicting Water Treatment Plant Chemical Doses

### 2025-12-11 Presentation DSCI445.Rmd
deleted GAM from contents

- Training and Testing
   - Training: 2018-2019
   - Testing: 2020
   - Approximately 70/30 split
- Coagulant Dose Prediction
   - Linear Regression
   - Tree-based Models
   - GAM
- Coagulant Dose Change Prediction
   - Linear methods: Multinomial, LDA
   - Nonlinear methods: QDA, Random Forest

>>>>

- Training and Testing
   - Training: 2018-2019
   - Testing: 2020
   - Approximately 70/30 split
- Coagulant Dose Prediction
   - Linear Regression Models
   - Tree-based Models
- Coagulant Dose Change Prediction
   - Linear methods: Multinomial, LDA
   - Nonlinear methods: QDA, Random Forest
